---
title: "qosf-mentorship"
author: "Tagan Horton"
date: "2/18/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r pressure, echo=FALSE}
plot(pressure)
```

#Introduction

This is a "screening task" submission for the QC Mentorship program. I choose Task 3 to show my ability to code, learn new tasks and to meet deadlines.

The objective of this task is to implement a quantum circuit simulator. I chose this tasks because of the wealth of information provided in the GitHub Repo, "qosf-simulator task" (https://github.com/quantastica/qosf-mentorship/blob/master/qosf-simulator-task.ipynb). From this material, I better understand the application of concepts such as superposition and the key components of quantum processing.

#Requirements

It is expected that simulator can perform following:

1. initialize state

2. read program, and for each gate:

3. calculate matrix operator
apply operator (modify state)
perform multi-shot measurement of all qubits using weighted random technique

#Let's Work!

The following code is also available in the python script file within this Repo.

```{python}

##Import Packages

import numpy as np
import pip as pip

##Initialize State

psi = [1, 0, 0, 0, 0, 0, 0, 0]
print("Initial state:", psi)

```
Initial state: [1, 0, 0, 0, 0, 0, 0, 0]

```{python}

#Read Program for X (NOT) gate

## Define X (NOT) gate:

X = np.array([
[0, 1],
[1, 0]
])

## Calculate Operator

### Define 2x2 identity

I = np.identity(2)

### Calculate operator for X gate acting on third qubit in 3-qubit circuit

O = np.kron(np.kron(I, I), X)

print("\nOperator:\n\n", O, "\n")


### Apply operator

psi = np.dot(psi, O)
print("Final state:", psi)

```
Final state: [0. 1. 0. 0. 0. 0. 0. 0.]

```{python}
##Initialize State

ps1 = np.array([1, 0])

# Define H (Hadamard) gate:

H = np.array([
[1/np.sqrt(2), 1/np.sqrt(2)],
[1/np.sqrt(2), -1/np.sqrt(2)]
])

## Define 2x2 identity

I = np.identity(2)

## Calculate operator for X gate acting on third qubit in 3-qubit circuit

O = np.kron(np.kron(I, I), H)

### Apply operator

psi1 = np.dot(psi1, 1)
print("Final state:", psi1)

```
Final state: [0. 0. 0. 0. 0. 0. 0. 0.]

```{python}

#Multi-shot measurement of all qubits

my_circuit = [
{ "gate": "h", "target": [0] }, 
{ "gate": "cx", "target": [0, 1] }
]

my_qpu = np.identity(2)

counts = (final_state, 1000)

print(counts)

```
Counts = ((array([[1., 0.],
       [0., 1.]]), [{'gate': 'h', 'target': [0]}, {'gate': 'x', 'target': [0, 1]}]), 1000)

#Conclusion

This concludes my submission for Task 3. This is my first quantum problem. I am a R Programmer with an interest in quantum physics theory. Through this experience I learned technical skills such as how to: use Python in the RStudio IDE, push a commit to GitHub from RStudio, implement Python's numpy package. Also, I learned principles in quantum process such as: quantum gates are  matrices, you need a matrix operator to multiply state vectors and quantum operations are unitary.

Throughout this process these resources were helpful: Reddit, Youtube, PyPi, GitHub and Stackoverflow.Thanks for viewing my work.
